---
title: "1105筆記"
author: "Annie"
date: "2024-11-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(animation)
library(ggplot2)
library (gganimate)
```


Loop is time consuming->reduce using loop
```{r}
for(i in 1:8) {
print("DILLIGAF")
print(i*i)
}
```
```{r}
demo <- seq (1,100,by=2) # sequence  1, 3, ..., 99
n<-length(demo) #  size of the foo sequence
demo.squared = NULL #  empty object

for (i in 1:n) { # our counter
  demo.squared[i] = demo[i]^2 # the task
}

demo.df<-data.frame(demo,demo.squared) 
plot (demo.df$demo~demo.df$demo.squared)

system.time(demo.squared2<-demo^2)
```
```{r}
demo.squared2<-demo^2
plot (demo~demo.squared2)
```
Recycling
```{r}
num_gen<-10  # no. generation
generation<-1:num_gen # create a variable generation
N <- rep (0,num_gen) #  "vector" of 10 zeros (could be `NULL`)
lambda <- 2 # growth rate
N[1] <- 2 # We need to set initial pop size
for (t in 1:(num_gen - 1)) { # the counter
  N[t+1]=lambda*N[t]  # task: double individuals
   }
plot(N~generation, type='b', col='blue', main='Discrete exponential growth') # the plot
```
Functin
```{r}
grow <- function (growth.rate) { # argument "growth.rate" of function "grow" 
num_gen<-10
generation<-1:num_gen
N <- rep (0,num_gen)
N[1] <- 1
for (t in 2:num_gen) { 
# not the use growth.rate argument and t-1  this time
  N[t]=growth.rate*N[t-1] 
}
  plot(N~generation,type='b', main=paste("Rate =", growth.rate)) 
}
```


Practice 6.1 Create a function called grow2 where both arguments: the growth.rate and number.generation can be “customized”.
```{r}
grow2 <- function (growth.rate, number.generation) { 
num_gen<-number.generation
generation<-1:num_gen
N <- rep (0,num_gen)
N[1] <- 1
for (t in 2:num_gen) { 

  N[t]=growth.rate*N[t-1] 
}
  plot(N~generation,type='b', main=paste("Rate =", growth.rate)) 
}


grow2(1.2,30)
```

Animation
```{r}
grow3 <- function (growth.rate) { 
  num_gen<-80
  generation<-1:num_gen
  N <- rep (0,num_gen)
  N[1] <- 1
  for (i in 2:num_gen) {
    N[i]=growth.rate*N[i-1]
  }
  plot(N~generation, xlim=c(0,10), ylim=c(0,100000), type='b', main=paste("Rate =", growth.rate))
}
```

```{r}
saveGIF({
for (i in 0:80){
  grow3(i)
}})
```

Practice 6.2 Write your own. The equation below illustrates a different kind of growth, the logistic growth:

Nt+1=Nt+[growth.rate∗Nt∗(100−Nt100)]

The 100 value is called the “carrying capacities” also called K, it means the population will be limited at 100 individuals. 
In your model the population will start with 10 individuals. 
You will then make the number of generation flexible using a function simulating population growth over 50 generations. 
You will further make this function flexible by changing growth.rate between 0.5 and 3.0. 

What do you observe? Save the outcome as a .gif if this works on your computer. Called me when you have the solution.
```{r}
grow3 <- function(growth.rate) { 
  num_gen <- 50
  generation <- 1:num_gen
  #growth.rates <- seq(0.5, 3.0, by = 0.1)
  N <- rep(0, num_gen)
  N[1] <- 10
  for (i in 2:num_gen) {
    N[i] = N[i - 1] + (growth.rate * N[i - 1] * ((100 - N[i - 1]) / 100))
  }
  plot(N ~ generation, type = 'b', main = paste("Rate =", growth.rate))
}

```

```{r}

saveGIF({
for (i in seq(0.5,3, by=0.1)){
  grow3(i)
}},interval=0.1)
```


```

