---
title: "Practice 4.1"
author: "Annie"
date: "2024-10-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

用Practice 2.3
```{r}
library (tidyr)
library(dplyr)
```


```{r}

rairuhuo<-
read.table('https://www.dipintothereef.com/uploads/3/7/3/5/37359245/rairuoho.txt', header=T, sep='\t') 

rairuhuo

rairuhuo_long <- rairuhuo %>%
  pivot_longer(day3:day8, names_to = "day", values_to = "length")
rairuhuo_long

rairuhuo_merge <- rairuhuo_long %>%
  unite("Plot", spatial1, spatial2, sep="_")
rairuhuo_merge

rairuhuo_merge$row<-NULL
rairuhuo_merge$column<-NULL
rairuhuo_merge
```
`
Using the rairuoho dataset you will use a ggplot2 visualization to show that over the course of the experiment 

the growth of the grass is becoming higher in the nutrient treatment than in the water treatment. 

You are free to use the visualization that you think makes the most sense 
Do not forget to embellish your visualization and the use of a legend and/or theme. 
The winner is the one who create the most informative and appealing plots. The price is that I will round up final score ;) You will send me a pdf file of the plot your made


```{r}
library(tidyverse)
library(dplyr)

chips <- rairuhuo_merge %>%
  group_by(day, treatment) %>%
  summarise(mean_length = mean(length, na.rm = TRUE), .groups = 'drop')

potato<- ggplot(data=rairuhuo_merge,aes(x=day,y=length, fill=treatment))+
  geom_boxplot(outlier.shape = NA, color = "#696969", show.legend =TRUE)+
  labs(title="Grass Growth:   Nutrient vs Water",subtitle = "2024.10.23",
    caption = "Source: Fun with R dataset")+ 
  scale_fill_manual(values=c("#FF9933", "#56B4E9", "#56B4E9"))+ 
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 16))+
  stat_summary(fun.y = mean, color = "#000000", position = position_dodge(0.75),
             geom = "point", shape = 18, size = 2,
             show.legend = FALSE)+
 geom_text(data = chips, aes(x = day, y = mean_length + 0.1, label = round(mean_length, 2)), 
            vjust = -5, color = "#404040", position = position_dodge(1.0))+
 theme(plot.background = element_rect(fill = "#F5F5DC"))+ 
  theme(
  panel.background = element_rect(fill = "#BAF7E9",
                                colour = "#BAF7E9",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "white")
  )
  
potato

ggsave(potato,filename = "Practice 4.2.pdf")
```



