---
title: "Practice 3.2"
author: "Annie"
date: "2024-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
summary(cars)
```



⚠ Practice 3.2 Create the following data frame from scratch. In this short and not very scientific experiment, the growth conditions of five plant individuals are to be tested. 

The height of the plants will be measured at the beginning of the experiment and after one week. The height is a double; the time of the measurement (start_experiment and end_experiment) and the individual plants (plant 1, plant 2,plant 3,plant 4 and plant 5) are character vectors. 

```{r}
plants <- c("plant 1", "plant 2","plant 3","plant 4","plant 5")
start_experiment <- c(4, 5, 3, 6, 7)
end_experiment <- c(9, 6, 5, 4, 7) 
df <- data.frame(plants, start_experiment, end_experiment)
df
```
Reformat this data frame to obtain the height into one single column and the time of the measurement as a factor with two levels. You save this data frame as the first element of a list named my.experiment.
做list中的第一個element,名為my.experiment
1. wide轉成long
2. 將start_experiment和end_experiment由character改成factor
3. 把這個data frame存成my.experiment的第一個element
```{r}
library(tidyr)

df_long <- df %>%
  pivot_longer(cols = c(start_experiment, end_experiment),
               names_to = "time",
               values_to = "height")


class(time)
mode(time)#測試time是什麼樣的character#阿為什麼是function
a <- c("start_experiment", "end_experiment")
typeof(a) # OMG變成 character了！！！
fact.time <- as.factor(a)
class(fact.time)# class factor
fact.time #查看 character values
attributes(fact.time) #有兩個 attributes: levels and class
levels(fact.time) #extract levels of a factor and the order

element1 <- list(df_long) #把這個data frame存成一個叫my.experiment的list
element1

class(element1[[1]]) #
str(element1)

```

The second element of this list will be another list called growth, in which three elements are stored: 
[1] a character vector extracting the row names of the previously created table ; 
[2] a numeric vector (double) indicating the change in height of each plant (can be positive or negative, but will be calculated as a percentage of the initial height); 
[3] a combination of these two elements in a table with two columns: plants and growth.

做list中的第二個element，which is名為growth的list
```{r}
#[1][2]
plants.name <- df$plants
initial.height<-element1$end_experiment
final.height<-element1$start_experiment
p<-c(end_experiment-start_experiment)/(start_experiment)*100
p
#[3] 
growth.table <- data.frame(
  plants = plants.name,
  growth = p
)

growth <- list(plants.name, p, growth.table)
growth

my.experiment<- list(element1, growth)

str(my.experiment) #查看each component’s structure

```

The third element of the my.experiment list will be an arbitrary message about the growth status of these plants
```{r}
message<-c("The growth status varies significantly among the plants, with some experiencing positive growth and others negative.")

my.experiment<- list(element1, growth, message)
my.experiment

str(my.experiment)
```

